### 2022-08-24 article.tex
Progress

Publishing raw code is already better than not publishing code at all,
as that raw code can reasonably be assumed to have run successfully at least once.
To reproduce an experiment from raw code can be painful, 
yet it is usually better than writing the same code from scratch.
In general, it appears that sharing code is rare \cite{stodden2011trust,read2015sizing}.

@@

There is another problem that authors of academic code face,
which is that they may be contacted with a user sending in a bug report.
HIERO
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead.
However, upon the find of a new bug, the question is:
does all the research that use that software still 
result in the same conclusions?
A code hosting website usually has a place to report bugs
that offer transparency in the handling of bug reports.

@@

Code is harder to preserve than an English text.

>>>>

Publishing raw code is already better than not publishing code at all,
as that raw code can reasonably be assumed to have run successfully at least once.
To reproduce an experiment from raw code can be painful, 
yet it is usually better than writing the same code from scratch.
In general, it appears that sharing code is 
rare \cite{stodden2011trust,read2015sizing},
with a pleasant exception being \cite{conesa2019making}.

@@

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).
However, upon the find of a new bug, the question is:
does all the research that use that software still 
result in the same conclusions?
A code hosting website usually has a place to report bugs
that offer transparency in the handling of bug reports.

@@

Code is harder to preserve than an English text
and preserving code is rarely done \cite{barnes2010publish}.
